Himalayan Expeditions Success Analysis

### 2024-04-14 paper/paper.qmd
Abstract added

---
title: "Himalayan Expeditions Success Analysis "
subtitle: "Analysis using data from Himalayan expeditions from 1905 through Spring 2019 leveraging Bayesian Logistic Regression"
author: Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/kaavyakalani26/himalayan-expeditions-analysis"
date: today
date-format: long
abstract: "Abstract"
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Himalayan Expeditions Success Analysis"
subtitle: "Analysis using data from Himalayan expeditions from 1905 through Spring 2019 leveraging Bayesian Logistic Regression"
author: Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: [https://github.com/kaavyakalani26/himalayan-expeditions-analysis](https://github.com/kaavyakalani26/himalayan-expeditions-analysis)"
date: today
date-format: long
abstract: "I analyse the relationship between different demographic, environmental and geographic factors and the successfulness of an attempt to summit a peak. Data from Himalayan expeditions in Nepal from 1905 through Spring 2019 is used and a Bayesian Logistic Regression model is leveraged to analyse the trends and factors influencing a successful summit. We find a strong relations between height of the peak, sex, age, season of expedition, if it was a solo ascent, and the success in summitting. This research provides insights into factors affecting the successfullness of an expedition to a summit and helps for future expedition planning, risk management, and safety protocols."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
